---
title: "Quarto Reporting Minimal Working Example"
format:
  html:
    theme: styles/brief.scss
    css:
      - styles/fontawesome/css/all.min.css
    toc: false
    page-layout: full
    pdf-engine: chromium
execute:
  echo: false
  warning: false
  message: false

extensions:
  - shafayetShafee/bsicons

params:
  report_date: "2026-01-01"
  fiscal_system: "state"
  period: "quarter"
---

# Quarto Reporting Minimal Working Example

```{r}
#| label: load-foo-data
#| eval: false
#| include: false

# This chunk is included to illustrate how to use the etl pipeline to load data
# and filter it for the relevant reporting period.

# # Set default fallback parameters for running code interactively during
# # development since Quarto params are only passed when rendering the document
# if (
#   !exists(
#     "params"
#   )
# ) {
#   params <- list(
#     report_date = "2026-01-01",
#     fiscal_system = "state",
#     period = "quarter"
#   )
# }

# # Load ETL output
# source(
#   "R/load_data.R"
# )

# # Run the function to load foo data
# foo_data <- load_foo_data()
```

```{r}
#| label: filter-foo-data
#| eval: false
#| include: false

# period <- reporting_period(
#   date = params$report_date,
#   system = params$fiscal_system,
#   period = "quarter"
# )

# start_date <- period$start
# end_date <- period$end

# foo_full_data <- foo_data$foo_full_data |>
#   dplyr::filter(
#     enrollment_starting_date >= start_date,
#     enrollment_starting_date <= end_date
#   )
```

## Callout Blocks in Quarto

Quarto supports several types of callout blocks to highlight information. These are built‑in and require no extensions. Callouts can contain text, code blocks, tables, or inline icons. However, note that callouts should be used for *concise* highlights. Do not place long lines of code in callout boxes because they do not break across pages by default.

### Basic Syntax

Callouts use the `:::` fence with a class. For example, the following is how to create a Note tip, used for sharing general information:

::: {.callout-note}
### Note
This is a note callout.
:::

````md
::: {.callout-note}
### Note
This is a note callout.
:::
````

### Other Types of Callouts

Below are examples of the main callout types that are available to supplement the Note callout shown above. Each shows the source code and the rendered output.

#### Tip - Helpful Hints

````md
::: {.callout-tip}
### Tip
This is a tip callout.
:::
````

::: {.callout-tip}
### Tip
This is a tip callout.
:::

#### Warning - Advice About Serious Issues

````md
::: {.callout-warning}
### Warning
This is a warning callout.
:::
````

::: {.callout-warning}
### Warning
This is a warning callout.
:::

#### Caution - Cautionary Advice About Potential Problems

````md
::: {.callout-caution}
### Caution
This is a caution callout.
:::
````

::: {.callout-caution}
### Caution
This is a caution callout.
:::

#### Important - Critical Information

````md
::: {.callout-important}
### Important
This is an important callout.
:::
````

::: {.callout-important}
### Important
This is an important callout.
:::

#### Overriding Titles

Titles can be added with a `title="..."` attribute to override the heading.

````md
::: {.callout-important title="Critical Deadline"}
This callout uses a custom title instead of the default “Important.”
:::
````

::: {.callout-important title="Critical Deadline"}
This callout uses a custom title instead of the default “Important.”
:::

### Cross-Referencing Callouts

To cross-reference a callout, add an ID attribute starting with the appropriate callout prefix. This allows one to reference a callout using the usual @ syntax.

````md
::: {#tip-cross-reference-example .callout-tip}
# Cross-Reference Guidance
Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-cross-reference-example...
````

This renders as:

::: {#tip-cross-reference-example .callout-tip}
# Cross-Reference Guidance

Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-cross-reference-example...

#### Callout Prefixes

Each callout type has a specific prefix for this purpose.

| Callout Type | Prefix |
|--------------|--------|
| note         | #nte-  |
| tip          | #tip-  |
| warning      | #wrn-  |
| important    | #imp-  |
| caution      | #cau-  |

### Callout Appearance Styles

Quarto supports three built‑in styles for callouts:

- **default** – full styling with border, background, and icon  
- **simple** – lighter styling with reduced border and background  
- **minimal** – text‑only, no header or background

#### Local (Per Callout)

You can set the style as an attribute on a single block:

````md
::: {.callout-tip appearance="default"}
### Default Tip
This callout uses the default style.
:::
````
::: {.callout-tip appearance="default"}
### Default Tip
This callout uses the default style.
:::

````md
::: {.callout-tip appearance="simple"}
### Simple Tip
This callout uses the simple style.
:::
````

::: {.callout-tip appearance="simple"}
### Simple Tip
This callout uses the simple style.
:::

````md
::: {.callout-tip appearance="minimal"}
### Minimal Tip
This callout uses the minimal style.
:::
````

::: {.callout-tip appearance="minimal"}
### Minimal Tip
This callout uses the minimal style.
:::

#### Global (All Callouts)

To apply a style to all callouts in a document, set the option in the YAML front matter:

````md
```yaml
format:
  html:
    callout-appearance: simple
  pdf:
    callout-appearance: minimal
```
````
### Icons in Callouts

By default, callouts include an icon, which vary by callout type. You can disable icons globally or locally.

#### Local (Per Callout)

Add icon=false to the block attributes:

````md
::: {.callout-note icon=false}
### Note Without Icon
This callout has no icon.
:::
````

::: {.callout-note icon=false}
### Note Without Icon
This callout has no icon.
:::

#### Global (All Callouts)

Set the option in the YAML front matter:

````md
---
format:
  html:
    callout-icon: false
  pdf:
    callout-icon: false
---
````

#### Enhancing Callouts With Additional Icons

Callouts can also be enhanced with icons for emphasis. For example, you may insert Font Awesome icons inline to visually distinguish tips, warnings, or highlights. See the [Font Awesome section](#font-awesome) later in this guide for detailed instructions on customizing icons (color, size, alignment) in both PDF and HTML outputs.

::: {.callout-tip}
### Workforce Trend
<i class="fa-solid fa-arrows-down-to-people icon-lg icon-primary"></i> Admissions are decreasing.
:::

## Basic Icon Usage

### Font Awesome 6

<i class="fa-solid fa-chart-line icon icon-md"></i>

### Bootstrap Icons

<i class="bi bi-person-standing-dress icon icon-md"></i>

Both use the same utility classes.

---

## Icon Sizes

Use one of the following:

| Class     | Size        | Use case          |
|-----------|-------------|-------------------|
| icon-xs   | very small  | inline labels     |
| icon-sm   | small       | table cells       |
| icon-md   | medium      | default           |
| icon-lg   | large       | section headers   |
| icon-xl   | extra large | hero metrics      |

### Extra Small Example:

<i class="fa-solid fa-users icon icon-xs"></i>

### Small Example:

<i class="fa-solid fa-users icon icon-sm"></i>

### Medium Example:

<i class="fa-solid fa-users icon icon-md"></i>

### Large Example:

<i class="fa-solid fa-users icon icon-lg"></i>

### Extra Large Example:

<i class="fa-solid fa-users icon icon-xl"></i>

---

## Icon Colors

| Class          | Color        | Use case          |
|----------------|--------------|-------------------|
| icon-primary   | blue         | default           |
| icon-secondary | gray         | neutral           |
| icon-muted     | light gray   | de‑emphasis       |
| icon-success   | green        | positive trend    |
| icon-warning   | gold         | caution           |
| icon-danger    | red          | negative trend    |

### Primary Example:

<i class="bi bi-graph-down icon icon-lg icon-primary"></i>

### Secondary Example:

<i class="bi bi-graph-down icon icon-lg icon-secondary"></i>

### Muted Example:

<i class="bi bi-graph-down icon icon-lg icon-muted"></i>

### Success Example:

<i class="bi bi-graph-down icon icon-lg icon-success"></i>

### Warning Example:

<i class="bi bi-graph-down icon icon-lg icon-warning"></i>

### Danger Example:

<i class="bi bi-graph-down icon icon-lg icon-danger"></i>

---

## Inline Alignment

Use `icon-inline` when placing an icon before text:

<i class="fa-solid fa-circle-info icon icon-inline icon-md"></i>
Important Note

---

## Panel Header Component

Use this pattern to create consistent section headerswith a **local rule** that does *not* span the full page:

```{=html}
<div class="panel-header">
  <div class="panel-header-main">
    <i class="fa-solid fa-arrows-down-to-people icon icon-lg icon-primary"></i>
    <span class="panel-title">Workforce Trend</span>
  </div>
  <div class="panel-header-rule"></div>
</div>
```

This produces:

- icon  
- title  
- a short rule aligned to the header  
- spacing that feels like a dashboard panel, not a page divider  

---

## Full Example

```{=html}
<div class="panel-header">
  <div class="panel-header-main">
    <i class="bi bi-people icon icon-lg icon-primary"></i>
    <span class="panel-title">Referral Overview</span>
  </div>
  <div class="panel-header-rule"></div>
</div>

<p>Referral volume increased by 12% this quarter.</p>
```
